Preprocessing

### 2023-08-31 analysis/preprocessing.Rmd
Update preprocessing.Rmd

@@

```{r}
d_journals <- d_journals %>% 
  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
         time_harmonized = case_when(
           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
           time_harmonized == "recent" ~ "Qualitative",
           time_harmonized == "recently published" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
           TRUE ~ time_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(review_harmonized = case_when(
           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           TRUE ~ review
         )) 
```

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = fct_recode(journal_empirical, T = "Yes", F = "No"),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
```

```{r}
d_articles <- d_articles %>%
  mutate(sample_id = factor(sample_id),
         article_id = factor(article_id),
         exclude = factor(exclusion_final),
         exclude_reason = factor(exclusion_reason_final),
         ppc_linked = fct_recode(ppc_linked_final, T = "NO", F = "YES")) %>%
  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
```

@@

```{r}
assert_that(
  all(d_journals$journal_empirical %in% c("Yes", "No")),
  msg = "Found unexpected values in journal_empirical column"
)
```

>>>>

d_journals %>%
  group_by(journal) %>%
  mutate(has_final = any(coder_id == "FINAL (TEH)"))

@@

```{r}
d_journals <- d_journals %>% 
  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
         time_harmonized = case_when(
           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
           time_harmonized == "recent" ~ "Qualitative",
           time_harmonized == "timely" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), timely scientific comments" ~ "Qualitative",
           time_harmonized == "recently published" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
           TRUE ~ time_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "a maximum of 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(review_harmonized = str_remove_all(review, pattern = '"'), #  remove any quotation marks
         review_harmonized = case_when(
           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           review == "NO, Strongly implied not, by this: \"The decision to publish is made by the Editors, in order to ensure a timely appearance in print. \"" ~ "NO",
           review == "YES, ...published work and may, after peer review, be published online as Matters Arising" ~ "YES",
           review == "YES, Commentaries will be subjected to peer-review and will be held to the same standards of providing a notable contribution to our field to warrant publication." ~ "YES",
           TRUE ~ review
         )) 
```

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
```

```{r}
d_articles <- d_articles %>%
  mutate(sample_id = factor(sample_id),
         article_id = factor(article_id),
         exclude = factor(exclusion_final),
         exclude_reason = factor(exclusion_reason_final),
         ppc_linked = as.logical(fct_recode(ppc_linked_final, T = "NO", F = "YES"))) %>%
  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
```

@@

```{r}
assert_that(
  all(d_journals$is_empirical %in% c(T,F)),
  msg = "Found unexpected values in is_empirical column"
)
```
